Response to Reviewers $Rev^1$

### 2020-03-10 ICT_Frontiers_rev202001_reply.tex
Move to local writing

% \input{ICT_Frontiers_rev202001.tex}
\documentclass[utf8]{article}
% \usepackage{import}
% \usepackage{RevisionToolsByAcer}
% \ProvidesPackage{RevisionToolsByAcer}
% \documentclass[utf8]{article}
% \ProvidesPackage{RevisionToolsByAcer}

%% Language and font encoding
\usepackage[english]{babel}
\usepackage[T1]{fontenc}

\usepackage{xr}
\externaldocument{ICT_Frontiers_rev202001}

% Sets page size and margins
% \usepackage[a4paper, top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=4cm]{geometry}
% \usepackage[papersize={10in, 12in}, top=3cm,bottom=2cm,left=2in,right=2in,marginparwidth=1.8in]{geometry}
\usepackage{titlesec}
\usepackage[dvipsnames,table,xcdraw]{xcolor}
\usepackage[at]{easylist}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{authblk}
\usepackage{float}
\usepackage{tikz}
\usepackage[threshold=2, autopunct=true, autostyle=true]{csquotes}

@@

% \revise
%   {Page}{original text}{revised text}
\newcommand{\revise}[3]{
    \noindent
    \newline
    \textbf{On page {#1}:}\newline
    \newline
    Original:\newline
    \textit{"#2"}
    \newline
    \newline
    Revised:\newline
    \textit{"#3"}\newline}
% =================================== Title ================================== %
\title{Response to Reviewers $Rev^1$}
\date{\today}
\author{}

@@

        \begin{ans}
            Dear Prof. Hoffman,
            Thank you for this interesting question. 
            There is no question that molecular complexes are coarse-grained objects of molecules through molecular recognition. Based on our hypothesis, if the dynamics of a molecular complex form an NTIC process, our theory (ICT) claims that the molecular complex is conscious. 
            We speculate that it may be easy to find informationally closed molecular complexes (isolated complexes) but may not be easy to find ones with NTIC. Nevertheless, this is a legible empirical question, and we look forward to discovering any self-assembly NTIC process at the molecular scales.
        \end{ans}

@@

        \begin{ans}
            TBD
        \end{ans}

@@

        \begin{ans}
            Yes. Because X is the micro-level of the universe, any coarse-graining of X (including E and S) should have equal or less information of X. Since Y is informationally closed with respect to X meaning that $X_t$ does not have more information about $Y_{t+1}$ than $Y_t$, any coarse-graining of X should also have equal or less information than $Y_t$. Therefore, Y is informationally closed with respect to X implying that Y is also informationally closed with respect to E and all other coarse-grainings of X.\\
            $\Delta t$
        \end{ans}

@@

@@

        \begin{question}
            Minor:
            \begin{itemize}
                \item "contributions to the field" This section is just a copy paste from the abstract and thus not necessarily helpful. Not sure though what the purpose of this section is meant to be by Frontiers.

@@

                \item $y_t$ corresponds to the content. I would argue that an activation state, without taking the system or relation between elements etc into account is meaningless and cannot capture/explain the structure of an experience. Though this issue can be dealt with at a later time.
            \end{itemize}
        \end{question}

@@

1. The coarse-graining idea seems undefined in critical ways, but the paper reads as though it is well-defined. So maybe the authors have compressed too much detail? In the formalism presented it is unclear what coarse-graining (or information closure to other grains) amounts to. With this lack of detail, it is then unclear to me why intermediate maxima in IC are a plausible result (why does IC not just decline with progressive coarse graining).

2. The idea of 'simulation'. This is a more minor point but I would appreciate if the authors could be clearer on this. It is arguable whether or not consciousness simulates anything (e.g. see Hoffman's interface theory); and some of the assertions the authors make re simulation seem unfounded anyways. But it could be that they mean something different or subtle (that consciousness is linked to or represents or etc the environment)

3. There were several other assertions that stood out to me as strange or wrong, but could be a matter of explanation or ignorance on my part (the feedforward system, the cut-apart system). Either way some more explanation would be good.
        \end{question}

        \begin{question}
            The English is not perfect and needs some good proofreading, though it was understandable throughout.

            On line 182, defining C-processes as cases where ‘Y is informationally closed to X’. This is now information closure in the sense of coarse-graining, but no such thing has been defined yet? Is it supposed to be so trivial that it is not required to make it explicit? To this point, closure is defined entirely in terms of system with respect to environment.

            Basically, I am not sure whether closer between scales is a matter of same-time (e.g. $I(Y_{t+1};X_{t+1})$) or across-time interactions ($I(Y_{t+1};X_t)$). Or could it be both?

            On line 241: “.. not sufficiently coarse-grained variables have low values of NTIC”, this is phrased as though it is necessarily true (and also that “we saw above”, though I do not see above where this is justified), but is it?

            At the very finest grain, wouldn’t even all the most ‘stochastic’ dynamics of a system be accounted for by prior states of the system, or by the environment? Why wouldn’t we assume that NTIC *only decreases* as the system is coarse-grained (as number of elements/states is decreased), for similar reasons as it must be zero at a 1-element 1-state system as the authors note? This seems an important point to be very clear on…

            on line 263: “NTIC processes encodes environmental information in its state. This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics.“

@@

            The ‘simulation’ notion is brought up again in section 5.2 (line 344), citing Bertschinger et al, though I do not find the idea in that paper.. I think authors need to be clearer on what they mean by ‘simulation’ to make this point.

            line 306: “Blindsight patients… make above chancel-level visual judgments without having any conscious perception about visual stimuli” I am not sure this characterization of blindsight is correct, it may be a matter of the phrasing. It could be - or probably is - the case that ‘blindsight’ patients always have some conscious experience of what drives their correct responses, but that the “visual character” of these experiences is degraded or missing.
            (Overgaard, Experimental Brain Research 2011)
            for a specific example
            (Mazzi, Bagattini, Savazzi; Frontiers in Psychology, 2016)

            on Line 316: On the issue of a feedforward network, the current state of a feedforward network with more than one layer is certainly driven by its own past states! So, mutual information of a feedforward network over a time lag should not be zero, unless I am misunderstanding something here?
             At the same time, I can see a version of the authors’ argument here - for a unit in a feedforward network with depth (distance-from-input) of N, a time lag of N time steps would always account fully for the states of the element. Is this the idea?

            on line 441: under the 'Prediction after system damaged', it is suggested that ICT predicts cutting a system in half would render both halves unconscious. But this would only be the case if neither half contains its own C-processes, yes? Since ICT allows that many C-processes can exist at the same time, it would have to be some special case for this prediction to hold true. So it seems to me the prediction is actually similar to that of IIT.

            Line 540: the theory doesn’t really seem to intend to solve the hard problem(s) at all, much less “completely solve”.

            I was expecting the problem of dreaming to come up in the last section (maybe along with SMC for which it is a serious problem). When dreaming the information between environment and the system is virtually zero; is this a problem for ICT? Also, more specific phenomena like the eigengrau - if you take away all visual input, for long enough, I do not lose my visual experiences - rather they take on a special state. Does ITC need to accept the possibility that even *trivial* IC can be a conscious process?        
        \end{question}

\end{document}

>>>>

% \input{ICT_Frontiers_rev202001.tex}
\documentclass[utf8]{article}
% \usepackage{RevisionToolsByAcer}
% \ProvidesPackage{RevisionToolsByAcer}
% \documentclass[utf8]{article}
% \ProvidesPackage{RevisionToolsByAcer}
%% Language and font encoding
\usepackage[english]{babel}
\usepackage[round, sort]{natbib}
\usepackage[T1]{fontenc}

% ============================ Sourcing main file ============================ %
\usepackage{xr}
\externaldocument{ICT_Frontiers_rev202001}
\usepackage{lineno}

% Sets page size and margins
% \usepackage[a4paper, top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=4cm]{geometry}
\usepackage[papersize={10in, 12in}, top=3cm,bottom=2cm,left=2in,right=2in,marginparwidth=1.8in]{geometry}
\usepackage{titlesec}
\usepackage[dvipsnames,table,xcdraw]{xcolor}
\usepackage[at]{easylist}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{authblk}
\usepackage{float}
\usepackage{tikz}
\usepackage[threshold=2, autopunct=true, autostyle=true]{csquotes}
\usepackage[colorinlistoftodos]{todonotes}

@@

% \revise
%   {Page}{original text}{revised text}
\newcommand{\revise}[3]{
	\newline
	\newline
    \noindent
    \textbf{line #1:}
    \newline
    Original:\newline
    \textit{"#2"}
    \newline
    \newline
    Revised:\newline
    \textit{"#3"}\newline}

% ================================ Annotation ================================ %
\newcommand{\toWrite}[1]{\noindent
	\textcolor{Orange}{\textbf{[[ #1 ]]}}}

% =================================== Title ================================== %
\title{Response to Reviewers $Rev^1$}
\date{\today}
\author{}

@@

        \begin{ans}
            Hi Prof. Hoffman,
            Thank you for your attention to our manuscript and your interesting question. \\
            There is no question that molecular complexes are coarse-grainings of molecules via molecular recognition. Based on our hypothesis, if the dynamics of a molecular complex is an NTIC process, the information closure theory of consciousness (ICT) would claim that the molecular complex has a certain degree of consciousness. Therefore, to your question, it is theoretically plausible under the framework of ICT. We speculate that it may be easy to find informationally closed molecular complexes (isolated complexes) but may not be easy to find ones forming NTIC processes. Nevertheless, with well-defined mathematical definition, this is an empirical and testable question to ICT. We look forward to learning any self-assembly process forming NTIC at molecular scales in the near future.        
        \end{ans}

@@

    	\begin{ans}
    		\newline
    		a) In one of the fomulations of NTIC, Equation 7, NTIC is the sum of  two terms: $I(Y_{t+1}; E_t)$ and $J_t(E -> Y)$. 
    		It is true that having high NTIC $I(Y_{t+1}; E_t)$ needs to be high. However, based on the setting in both Bertschinger et al. 2006 and our Section 2 (from Line \lineref{line:r1q1a}),  if $Y_t$ does not have information $J_t(E -> Y)$

    		In the video camera example that the reviewer proposed, we can consider two cases. If the sensory information extracted by the camera is only partially predictive to the (predictive information \citep{bialek2001predictability} is small).

    		We then consider the other case which the environment E is deterministic and fully observable. If $H(E_{t+1|E_t}=0$ 
    		It is true that simply copy the entire environment state to $Y$ will yield 
    		$I(Y_{t+1}; E_t)>0$ and $J_t(E -> Y)=0$.

    		$I(Y_{t+1}; E_t)$ will be large. However, 
    		\\
    		\toWrite{Don't know how much to write there}

    		b) Thank the reviewer for this outstanding question. 
    		Actually, we are currently working on state-dependent formulations of ICT. 
    		In this first version of ICT, we did not use state-dependent formulations. 
    		However, we do think a state-dependent measurement is important to describe the conscious experience. 
    		We have been working on a state-dependent version of NTIC using point-wise informational measurements. 
    		We have been planning to propose state-dependent ICT in our next version. 
    		We have added a short paragraph about this issue at Line \lineref{line:r1-state-dep}.
    		\toWrite{add a short para}

    	\end{ans}

@@

        \begin{ans}
            Yes. Because X is the micro-level of the universe, any coarse-graining of X (including E and S) should have equal or less information of X. Since Y is informationally closed with respect to X meaning that $X_t$ does not have more information about $Y_{t+1}$ than $Y_t$, any coarse-graining of X should also have equal or less information than $Y_t$. Therefore, Y is informationally closed with respect to X implying that Y is also informationally closed with respect to E and all other coarse-grainings of X.\\
            $\Delta t$ regards to the temporal coarse-graining and, therefore, determines the temporal scale that form higher NTIC. It's true that the 
            \toWrite{Something here}\\
			In our current version, NTIC was proposed because we attribute both closureness $-I(Y_{t+1}; E_t|Y_t)$ and non-triviality $I(Y_{t+1}; E_t) = 0$. 
			$I(Y_{t+1}; E_t|Y_t) = 0$ is not necessary. 
			\toWrite{Really difficult to say this part}

        \end{ans}

@@

    	\begin{ans}
    		\toWrite{Maybe this needs to be written together with previous reply.}
    	\end{ans}

@@

    	\begin{ans}
    		\toWrite{Add something here}
    		We have added a paragraph at Line \lineref{line:dream}
    	\end{ans}

        \begin{question}
            Minor:
            \begin{enumerate}
                \item "contributions to the field" This section is just a copy paste from the abstract and thus not necessarily helpful. Not sure though what the purpose of this section is meant to be by Frontiers.

@@

                \item $y_t$ corresponds to the content. I would argue that an activation state, without taking the system or relation between elements etc into account is meaningless and cannot capture/explain the structure of an experience. Though this issue can be dealt with at a later time.
            \end{enumerate}
        \end{question}

    	\begin{ans}
    		\begin{enumerate}
    			\item It's true that we were also confused about it during submission. 
    			We have modified this as follows: \\
    			\toWrite{"contributions to the field"}

    			\item Thank the reviewer for this suggestion. We have modified our manuscript and cited  the reference at Line \lineref{line:lack-theory}. \toWrite{Change main text}

    			\item We fully agree with the reviewer's comment. 
    			In fact, in our theory, we do not partition states of processes into activation and relation. For example, both activation and structure states of a neural network should be considered. After all, they can be parameterised as the parameters of processes. The only difference is the temporal scales of parameter changes. States of activation may have more rapid dynamics than states of relation. In ICT, this difference is crucially related to the temporal coarse-graining which we did not address in this article but can be easily generalised in future versions of ICT.

    			\toWrite{To write something in the main text?}

    		\end{enumerate}

    	\end{ans}

@@

			\begin{enumerate}
				\item The coarse-graining idea seems undefined in critical ways, but the paper reads as though it is well-defined. So maybe the authors have compressed too much detail? In the formalism presented it is unclear what coarse-graining (or information closure to other grains) amounts to. With this lack of detail, it is then unclear to me why intermediate maxima in IC are a plausible result (why does IC not just decline with progressive coarse graining).

				\item The idea of 'simulation'. This is a more minor point but I would appreciate if the authors could be clearer on this. It is arguable whether or not consciousness simulates anything (e.g. see Hoffman's interface theory); and some of the assertions the authors make re simulation seem unfounded anyways. But it could be that they mean something different or subtle (that consciousness is linked to or represents or etc the environment)\todo{I don't understand this question well}

				\item There were several other assertions that stood out to me as strange or wrong, but could be a matter of explanation or ignorance on my part (the feedforward system, the cut-apart system). Either way some more explanation would be good.
			\end{enumerate}
        \end{question}

    	\begin{ans}
    		\begin{enumerate}
    			\item In this article, the definition of coarse-graining is our "Definition 1" (line: \lineref{line:r2q1-1}) which is simply a function mapping a stochastic process $X$ with state space $\mathcal{X}$ to a stochastic process $Y$ with state space $\mathcal{Y}$.
    			We do not specify any specific types of coarse-graining.
    			\toWrite{Instead, our hypothesis states that any process which coarse-graining which}

    			We emphasise the non-monotonic relation between the scales of coarse-graining and the degrees of NTIC. However, we do not exclude the possibility that there exist multiple NTIC picks across scales of coarse-graining of a process. 
    			This implies that we do not exclude the possibility that there exist multiple high conscious processes at different scales. 
    			(However, due to IC, conscious processes are not able to know the existence of each other. 
					\todo{Discuss this}

    			\item \toWrite{TBD}
    			\item \toWrite{After replying the first reviewer}
    		\end{enumerate}

    	\end{ans}

        \begin{question}
			The English is not perfect and needs some good proofreading, though it was understandable throughout.
        \end{question}

    	\begin{ans}
    		\todo{What should we deal with this?}
    	\end{ans}

    	\begin{question}
			On line 182, defining C-processes as cases where ‘Y is informationally closed to X’. This is now information closure in the sense of coarse-graining, but no such thing has been defined yet? Is it supposed to be so trivial that it is not required to make it explicit? To this point, closure is defined entirely in terms of system with respect to environment.

			Basically, I am not sure whether closer between scales is a matter of same-time (e.g. $I(Y_{t+1};X_{t+1})$) or across-time interactions ($I(Y_{t+1};X_t)$). Or could it be both?    		
    	\end{question}

    	\begin{ans}
			Here, we followed a common setup of coarse-graining (e.g. \toWrite{cite here}), which does not take time $Y_t=f_Y(X_t)$ (in Definition 1). In this setup, coarse-graining is unidirectional ad does not involve interaction between scales. This means that coarser scales supervene on finer scales, and there exists no top-down causation. \\
			In our hypothesis, Y is IC with respect to the microstate of the universe, X. This is critical in the hypothesis because Y is IC with respect to X, implying that Y is also IC with respect to its intermediate level S and its environment E in Fig. \ref{fig:fullgraph}.\todo{need any change in the main text?}
    	\end{ans}

    	\begin{question}            
    		On line 241: “.. not sufficiently coarse-grained variables have low values of NTIC”, this is phrased as though it is necessarily true (and also that “we saw above”, though I do not see above where this is justified), but is it?

    		At the very finest grain, wouldn’t even all the most ‘stochastic’ dynamics of a system be accounted for by prior states of the system, or by the environment? Why wouldn’t we assume that NTIC *only decreases* as the system is coarse-grained (as number of elements/states is decreased), for similar reasons as it must be zero at a 1-element 1-state system as the authors note? This seems an important point to be very clear on…
    	\end{question}

    	\begin{ans}
    		\toWrite{The reviewer is right?}
    		Thank the reviewer for this critical comment. It is true that NTIC a monotonic function of scales of coarse-graining. NTIC can increase or decrease when the grains are coarser. We are currently still working on the relationship between scales and NTIC. 
    		We will systematically address NTIC and functions of coarse-graining in our following studies. 
    		Further more, in our current analysis, it seems that this is also related to informational synergy and redundancy. We aim for presenting the core concept of ICT in this article.
    		The reviewer's critical question is on our list of future work. 
    		\toWrite{Need to change the text a lot!!}
    	\end{ans}

    	\begin{question}
    		on line 263: “NTIC processes encodes environmental information in its state. This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics.“

@@

    		The ‘simulation’ notion is brought up again in section 5.2 (line 344), citing Bertschinger et al, though I do not find the idea in that paper.. I think authors need to be clearer on what they mean by ‘simulation’ to make this point.
    	\end{question}

    	\begin{ans}
    		Thank the reviewer for this mindful comment. 
    		Our description indeed is not clear enough. The environmental information here about not only states but also state transitions. 
    		This is because high NTIC implies high mutual information between a process and its environment $I(Y_{t+1};E_t)$ (Eq. \ref{eq:nticObjective2}). Therefore, the dynamics of the process $Y$ needs to covary with the dynamics of its environment $E$. Here, we consider 'simulation' is a more precise expression than 'encoding'. 
    		The notion of simulation is the same as the 'Modeling' case on Page 4 in Bertschinger et al. , 2006: \\
    		\textit{"B2)~Modeling: The system reaches synchronization and internalizes the correlations observed in the environment by building up own structures."}
    		\\ \toWrite{add something in the main text}
    	\end{ans}

   	\begin{question}
			line 306: “Blindsight patients… make above chancel-level visual judgments without having any conscious perception about visual stimuli” I am not sure this characterization of blindsight is correct, it may be a matter of the phrasing. It could be - or probably is - the case that ‘blindsight’ patients always have some conscious experience of what drives their correct responses, but that the “visual character” of these experiences is degraded or missing.
			(Overgaard, Experimental Brain Research 2011)
			for a specific example
			(Mazzi, Bagattini, Savazzi; Frontiers in Psychology, 2016)
    	\end{question}

   		\begin{ans}
   			Thank the reviewer for the clarification. 
   			Yes, we specifically address the visual character of their experience.
   			We have changed our sentence as follows:
   			\revise{\lineref{line:r2q6}}
   			{
   				Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements without having any conscious perception about visual stimuli.
   			}
   			{
   				Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements when their visual experiences is degraded or missing (however, they may still preserve some forms of conscious experience, see \cite{overgaard2011visual, mazzi2016blind}). 
   			}
   		\end{ans}

    	\begin{question}
            on Line 316: On the issue of a feedforward network, the current state of a feedforward network with more than one layer is certainly driven by its own past states! So, mutual information of a feedforward network over a time lag should not be zero, unless I am misunderstanding something here?
			At the same time, I can see a version of the authors' argument here - for a unit in a feedforward network with depth (distance-from-input) of N, a time lag of N time steps would always account fully for the states of the element. Is this the idea?		
    	\end{question}

 		\begin{ans}
 			Thank the reviewer for this valuable comment. 
 			Indeed, 
 			\\
 			\toWrite{This is really a good question.}
 			\todo{Indeed, if information is just copied to the process, it will still be NTIC. Feedforward is just a way to copy the information}
 		\end{ans}

    	\begin{question}
    		on line 441: under the 'Prediction after system damaged', it is suggested that ICT predicts cutting a system in half would render both halves unconscious. But this would only be the case if neither half contains its own C-processes, yes? Since ICT allows that many C-processes can exist at the same time, it would have to be some special case for this prediction to hold true. So it seems to me the prediction is actually similar to that of IIT.
    	\end{question}

    	\begin{ans}
    		Thank the reviewer for this considerate comment. The reviewer is correct. This prediction is under an assumption which we did not explicitly specify in our last version. We assume that we have one conscious (NTIC) process involving information in both brain hemispheres. Namely, the process is informationally closed only when we consider the information in both hemispheres. We agree that if both hemispheres have their own NTIC proceess ICT should predict no change of conscious experience before and after cutting. Cutting should not make any difference because they are informationally closed with respect to each other. We also agree that this prediction is relatively premature. However, we also acknowledge the strength of all computational theories of consciousness. The reviewer's question is empirical to us under formal mathematical formulations of ICT and IIT. Systematical comparisons between model predictions can be done by rigorous modelling studies in the future.

    		\toWrite{The original paragraph has been changed as follows: lline \lineref{line:r2-cutting}:}
    	\end{ans}

        \begin{question}                                                                   
            Line 540: the theory doesn’t really seem to intend to solve the hard problem(s) at all, much less “completely solve”.            
            I was expecting the problem of dreaming to come up in the last section (maybe along with SMC for which it is a serious problem). When dreaming the information between environment and the system is virtually zero; is this a problem for ICT? Also, more specific phenomena like the eigengrau - if you take away all visual input, for long enough, I do not lose my visual experiences - rather they take on a special state. Does ITC need to accept the possibility that even *trivial* IC can be a conscious process?
        \end{question}

    	\begin{ans}
    		ICT is our first attempt to approach the hard problem of consciousness. We hope that ICT and our following works can establish an informational perspective on conscious experience. Instead of solving the hard problem of consciousness, we more look forward to mathematically determining whether the hard problem can be solved or not by information theory. However, because the relevant discussion is clearly outside the scope of this article, we prefer not to discuss the hard problem here. n

    		It is important to note that we reckon only part of the neural system is involved in the NTIC process(es). This is due to the fact that some parts of the neural system are evidently not informationally closed. They only passively react to sensory inputs or other parts of the neural system. 
    		To the NTIC process(es), the rest of the neural system is considered as the environment. This notion is shortly indicated at line \lineref{line:neu-env}.
    		We speculate that, during dreaming, the neural system can still form the NTIC process(es) with respect to other parts of the neural system which we know they maintain high activities. The same idea can be also applied to phenomena like Eigengrau. However, at the current stage, this is mere speculation so we restrained ourself from making the statement in our last version of the manuscript. However, thank the reviewer for bringing up this question. We believe that it is still worth to mention issues about dreaming. We have added a short paragraph as follows:

    		\toWrite{add something in the main text at Line \lineref{line:dream}}

    		Finally, we believe that this is also a clear empirical question that can be tested in future studies. 
    	\end{ans}

	\bibliography{ref}
\end{document}
